### 2021-02-04 ch05_paper_ecs/paper_ecs.tex
Added further tables for chapter 05 and text for chapter 06

One of the most important sources of information for this purpose is
undoubtedly observational data. As presented in
\cref{subsec:02:emergent_constraints}, emergent constraints are a beneficial
tool to assess the accuracy of climate model projections and reduce associated
uncertainties with appropriate observations of the Earth system. For \ac{ECS},
a large variety of different emergent constraints has been developed over the
years, which we now evaluate on the new \acs{CMIP}6 ensemble. In total we
assess eleven emergent constraints (selected by their availability in the
\ac{ESMValTool}), out of which the most are related to cloud feedbacks, since
these constitute the most important source of uncertainty for \ac{ECS}
\commentcite{Boucher2013, Flato2013}{see also
  \cref{subsec:02:climate_feedbacks}}. Since all of the evaluated emergent
constraints have been derived on the \acs{CMIP}3 or \ac{CMIP}5 ensemble, the
\ac{CMIP}6 models offer an exciting possibility to perform out-of-sample
testing using the previously unseen data. We quantify the skill of the emergent
constraints with three metrics: the coefficient of determination $R^2$ of the
linear relationship, the statistical significance using a two-sided $t$-test
based on the Pearson correlation coefficient $r$ (see \cref{eq:02:t}) and the
constrained range of \ac{ECS} based on the constrained \ac{PDF} (see
\cref{eq:02:pdf_y_given_x0}). This analysis has already been published in
\textcite{Schlund2020a}. For this paper, the author of this thesis lead the
writing and the analysis and contributed the code to reproduce this analysis
including all figures and tables with the \ac{ESMValTool}. In this chapter, we
first introduce the eleven emergent constraints on \acs{ECS} and evaluate them
on \acs{CMIP}5 and \acs{CMIP}6 data
(\cref{sec:05:comparison_of_emergent_constraints}). After that, we provide a
discussion of the results and draw important conclusions from them
(\cref{sec:05:discussion_and_conclusions}).

@@

\section{Discussion and Conclusions}
\label{sec:05:discussion_and_conclusions}

- mention limitation of emergent constraints of chapter 2 again

- mention why significance

- it is not possible to constrain ECS with the emergent constraints

>>>>

One of the most important sources of information for this purpose is
undoubtedly observational data. As presented in
\cref{subsec:02:emergent_constraints}, emergent constraints are a beneficial
tool to assess the accuracy of climate model projections and reduce associated
uncertainties with appropriate observations of the Earth system. For \ac{ECS},
a large variety of different emergent constraints has been developed over the
years, which we now evaluate on the new \acs{CMIP}6 ensemble. In total we
assess eleven emergent constraints (selected by their availability in the
\ac{ESMValTool}), out of which the most are related to cloud feedbacks, since
these constitute the most important source of uncertainty for \ac{ECS}
\commentcite{Boucher2013, Flato2013}{see also
  \cref{subsec:02:climate_feedbacks}}. Since all of the evaluated emergent
constraints have been derived on the \acs{CMIP}3 or \ac{CMIP}5 ensemble, the
\ac{CMIP}6 models offer an exciting possibility to perform out-of-sample
testing using the previously unseen data. We quantify the skill of the emergent
constraints with three metrics: the coefficient of determination $R^2$ of the
linear relationship, the statistical significance using a two-sided $t$-test
based on the Pearson correlation coefficient $r$ (see \cref{eq:02:t}) and the
constrained range of \ac{ECS} based on the constrained \ac{PDF} (see
\cref{eq:02:pdf_y_given_x0}). This analysis has already been published in
\textcite{Schlund2020a}. For this paper, the author of this thesis lead the
writing and the analysis and contributed the code to reproduce this analysis
including all figures and tables with the \ac{ESMValTool}. In this chapter, we
first introduce the methods and data (climate model output and observations)
used in this study (\cref{sec:05:methods_and_data}). After that, we present the
eleven emergent constraints on \acs{ECS} and evaluate them on the \acs{CMIP}5
and \acs{CMIP}6 ensemble (\cref{sec:05:comparison_of_emergent_constraints}).
Finally, we provide a discussion (\cref{sec:05:discussion}) and a summary of
the results (\cref{sec:05:summary}).

\section{Methods and Data}
\label{sec:05:methods_and_data}

In this study we use the output from climate models participating in
\acs{CMIP}5 and \acs{CMIP}6, shown in \cref{sec:app:cmip_models_in_chapter_5}
in \cref{tab:app:a:cmip5_models,tab:app:a:cmip6_models}, respectively.

@@

\section{Discussion}
\label{sec:05:discussion}

\section{Summary}
\label{sec:05:summary}

### 2021-02-04 ch06_paper_gpp/paper_gpp.tex
Added further tables for chapter 05 and text for chapter 06

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                                  Paper ECS                                  %
%=============================================================================%

\chapter{Evaluation of Emergent Constraints on ECS in CMIP6}
\label{ch:paper_ecs}

>>>>

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                                  Paper GPP                                  %
%=============================================================================%

\chapter{Constraining Future \acl{GPP} with Machine Learning}
\label{ch:06:paper_gpp}

- Single-process emergent constraints have disadvantages

To overcome these, we explore an alternative approach that expands the MDER
method with an ML algorithm. In contrast to emergent constraints, this approach
considers (1) multiple process-based predictors, (2) multi-dimensional
(gridded) target variables and (3) non-linear relationships between the
predictors and the target variable. The target variable analyzed is GPP. As
described in detail in section XXX, the carbon cycle slows down global warming
by absorbing 30 \% CO2, thus accurately quantifying the carbon sink is crucial.
GPP is most largest flux of the terrestrial carbon cycle. Due to feedbacks
(section XXX, NAME OF FEEDBACKS), multi-model projectionf of future GPP is
uncertain, especially in CMIP5 RCP 8.5 at the end of the century. Thus, the aim
of the works presented in this chapter is to reduce uncertainties in
multi-model projections of future GPP in the RCP 8.5 scenario at the end of the
21st century with a new ML-based weighting technique and observations. The new
two‐step approach utilizes aspects of emergent constraints and the MDER
technique in combination with a supervised machine learning algorithm. In the
first step, we apply an existing emergent... (see SCHLUND ET AL., 2020).

\section{Step 1: XXXXXXXXXXXXXXXXXX}
\label{sec:06:step_1}

### 2021-02-04 end_appendix/appendix.tex
Wrote first page of introduction
Added first figure
Finished section on carbon cycle
Added tables that summarizes changes made to the ESMValCore
Added figures for ESMValTool contributions (chapter 3)
Added further tables for chapter 05 and text for chapter 06

\renewcommand{\thesection}{\Alph{section}}

\section{TBA}

TBA.

\section{TBA}

TBA.

>>>>

\begingroup

\crefalias{section}{appendix}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}
\renewcommand{\thesection}{\Alph{section}}

\section{Overview of \acs{CMIP} Models used in
  \texorpdfstring{\Cref{ch:05:paper_ecs}}{Chapter \ref{ch:05:paper_ecs}}}
\label{sec:app:cmip_models_in_chapter_5}

\Cref{tab:app:a:cmip5_models,tab:app:a:cmip6_models} give an overview over the
\acs{CMIP}5 and \acs{CMIP}6 models, respectively, which are used for the
evaluation of emergent constraints on \ac{ECS} \autocite{Schlund2020a} as
presented in \cref{ch:05:paper_ecs}.

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Model & Index & Main reference \\
    \midrule
    ACCESS1-0 & 1 & \textcite{Dix2013} \\
    ACCESS1-3 & 2 & \textcite{Dix2013} \\
    BNU-ESM & 3 & \textcite{Ji2014} \\
    CCSM4 & 4 & \textcite{Gent2011, Meehl2012} \\
    CNRM-CM5 & 5 & \textcite{Voldoire2013} \\
    CNRM-CM5-2 & 6 & \textcite{Voldoire2013} \\
    CSIRO-Mk3-6-0 & 7 & \textcite{Rotstayn2012} \\
    CanESM2 & 8 & \textcite{Arora2011} \\
    FGOALS-g2 & 9 & \textcite{Li2013} \\
    GFDL-CM3 & 10 & \textcite{Donner2011} \\
    GFDL-ESM2G & 11 & \textcite{Dunne2012} \\
    GFDL-ESM2M & 12 & \textcite{Dunne2012} \\
    GISS-E2-H & 13 & \textcite{Schmidt2006} \\
    GISS-E2-R & 14 & \textcite{Schmidt2006} \\
    HadGEM2-ES & 15 & \textcite{Collins2011} \\
    IPSL-CM5A-LR & 16 & \textcite{Dufresne2013} \\
    IPSL-CM5A-MR & 17 & \textcite{Dufresne2013} \\
    IPSL-CM5B-LR & 18 & \textcite{Dufresne2013} \\
    MIROC-ESM & 19 & \textcite{Watanabe2011} \\
    MIROC5 & 20 & \textcite{Watanabe2010} \\
    MPI-ESM-LR & 21 & \textcite{Giorgetta2013} \\
    MPI-ESM-MR & 22 & \textcite{Giorgetta2013} \\
    MPI-ESM-P & 23 & \textcite{Giorgetta2013} \\
    MRI-CGCM3 & 24 & \textcite{Yukimoto2012} \\
    NorESM1-M & 25 & \textcite{Bentsen2013, Iversen2013} \\
    bcc-csm1-1 & 26 & \textcite{Wu2014} \\
    bcc-csm1-1-m & 27 & \textcite{Wu2014} \\
    inmcm4 & 28 & \textcite{Volodin2010} \\
    \bottomrule
  \end{tabulary}
  \caption{List of \acs{CMIP}5 models used in \cref{ch:05:paper_ecs} alongside
    the main reference and the index used in the corresponding figures.
    \AdaptedFrom{Schlund2020a}.}
  \label{tab:app:a:cmip5_models}
\end{table}

\begin{table}[p]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Model & Index & Main reference \\
    \midrule
    ACCESS-CM2 & 29 & \textcite{Bi2013} \\
    ACCESS-ESM1-5 & 30 & \textcite{Law2017, Ziehn2017} \\
    AWI-CM-1-1-MR & 31 & \textcite{Rackow2018, Sidorenko2015} \\
    BCC-CSM2-MR & 32 & \textcite{Wu2019} \\
    BCC-ESM1 & 33 & \textcite{Wu2019} \\
    CAMS-CSM1-0 & 34 & \textcite{Rong2018} \\
    CAS-ESM2-0 & 35 & \textcite{Wang2020} \\
    CESM2 & 36 & \textcite{Danabasoglu2020} \\
    CESM2-FV2 & 37 & \textcite{Danabasoglu2020} \\
    CESM2-WACCM & 38 & \textcite{Danabasoglu2020, Gettelman2019a} \\
    CESM2-WACCM-FV2 & 39 & \textcite{Danabasoglu2020, Gettelman2019a} \\
    CMCC-CM2-SR5 & 40 & \textcite{Cherchi2019} \\
    CNRM-CM6-1 & 41 & \textcite{Voldoire2019} \\
    CNRM-CM6-1-HR & 42 & \textcite{Voldoire2019} \\
    CNRM-ESM2-1 & 43 & \textcite{Seferian2019} \\
    CanESM5 & 44 & \textcite{Swart2019} \\
    E3SM-1-0 & 45 & \textcite{Golaz2019} \\
    EC-Earth3-Veg & 46 & \textcite{Wyser2020} \\
    FGOALS-f3-L & 47 & \textcite{Guo2020, He2019, He2020} \\
    FGOALS-g3 & 48 & \textcite{Li2020} \\
    GISS-E2-1-G & 49 & \textcite{Rind2020} \\
    GISS-E2-1-H & 50 & \textcite{Rind2020} \\
    HadGEM3-GC31-LL & 51 & \textcite{Kuhlbrodt2018} \\
    HadGEM3-GC31-MM & 52 & \textcite{Williams2018} \\
    INM-CM4-8 & 53 & \textcite{Volodin2017,Volodin2017a} \\
    INM-CM5-0 & 54 & \textcite{Volodin2017,Volodin2017a} \\
    IPSL-CM6A-LR & 55 & \textcite{Boucher2020} \\
    KACE-1-0-G & 56 & \textcite{Lee2020} \\
    MCM-UA-1-0 & 57 & \textcite{Delworth2002} \\
    MIROC-ES2L & 58 & \textcite{Hajima2020} \\
    MIROC6 & 59 & \textcite{Tatebe2019} \\
    MPI-ESM-1-2-HAM & 60 & \textcite{Mauritsen2019} \\
    MPI-ESM1-2-HR & 61 & \textcite{Muller2018} \\
    MPI-ESM1-2-LR & 62 & \textcite{Mauritsen2019} \\
    MRI-ESM2-0 & 63 & \textcite{Yukimoto2019} \\
    NESM3 & 64 & \textcite{Cao2018} \\
    NorCPM1 & 65 & \textcite{Counillon2016} \\
    NorESM2-LM & 66 & \textcite{Seland2020} \\
    NorESM2-MM & 67 & \textcite{Seland2020} \\
    SAM0-UNICON & 68 & \textcite{Park2019} \\
    TaiESM1 & 69 & \textcite{Lee2020a} \\
    UKESM1-0-LL & 70 & \textcite{Sellar2019} \\
    \bottomrule
  \end{tabulary}
  \caption{As in \cref{tab:app:a:cmip5_models}, but for the \acs{CMIP}6 models
    used in \cref{ch:05:paper_ecs}. \AdaptedFrom{Schlund2020a}.}
  \label{tab:app:a:cmip6_models}
\end{table}

\endgroup
